The problem and promise of scale in multilayer animal social networks

### 2020-02-11 paper/manuscript.Rmd
rm old bullet results

# Scale in multilayer networks in practice: case study results and discussion
<!-- TODO: Add intro/general to results? with mention figures are means of inds-->

<!-- TODO: make sure we clarify these are means of all individuals? -->

<!-- TODO: discuss layer similarity for social threshold -->
In general, individuals in multilayer networks became more connected as social
scale increased; however, this relationship varied by habitat type and season.
As social scale increased, graph strength for winter networks increased to
~100-200 m thresholds, followed by a plateau, while graph strength for summer
networks did not change as the social threshold increased (Figure
\@ref(fig:socres)a). Layer relevance increased for winter networks between 5 and
50 m social thresholds, then did not change for any habitat types which suggests
the winter habitat layers captured most, if not all, of the potential
connections an individual would have across these networks (Figure
\@ref(fig:socres)b). <!-- missing summer--> Connective redundancy increased
rapidly when groups were formed up to ~100 m threshold, followed by
a plateau and slight decrease at higher thresholds, presumably due to an
increase in summer forest degree at ~500 m (Figure \@ref(fig:socres)d). Taken
together, these results suggest the optimal social scale at which groups should
be assigned is likely somewhere between ~20-100 m based on the rate at which
network metrics stabilized. For ungulates, groups are often assigned based on 50
m threshold (Lingle 2003; Lesmeries et al. 2018; Peignier et al. 2019),
suggesting that given similar quantities of data, ~50 m is likely an ideal
social scale for generating social networks in caribou and similar species.

<!-- landcover resolution
* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
* decreasing winter lichen relevance because the degree + number of edges decreased
--> 
<!-- TODO: discuss things in a,b,c,d order consistently. They shouldn't be presented out of order -->
Increasing the scale of landcover resolution resulted in decreased proportion of
rare and patchy habitats, and low connectivity of individuals in these habitats.
In winter, layer relevance was stable for open and forest habitats but decreased
for forage habitats (Figure \@ref(fig:lcres)b). Layer similarity was generally
stable for forest and open habitats except for a contrasting increase in
similarity for forest and decrease in similarity for open habitats 250 m
landcover resolution (Figure \@ref(fig:lcres)c). Layer similarity was not
possible to calculate between winter and summer forage because, at all landcover
resolutions greater than 30 m there were no individuals connected in the network
layers. <!-- individuals still used forage but in much lower proportion +
lowered opportunity to associate --> Connective redundancy decreased with
increasing landcover resolution due the decrease in connectivity of individuals
in winter forage habitats, resulting in a multilayer network where neighbours
were less frequently repeated in multiple layers <!-- TODO: I'm having a hard
time understanding this previous sentence --> (Figure\@ref(fig:lcres)d).  These
results indicate the importance of matching landcover resolution to scale of
selection as well as ensuring the landcover product used has a resolution fine
enough to detect relevant landscape features and habitats. <!-- TODO: how? This
isn't clear enough for me to follow yet -->

<!-- nobs * common, though at different points - more observations until
stabilizing * we dont see the stabilizing/full plateau for connective redundancy
but appears to be coming.. * still some variability, especially for graph
strength because individuals are differently connected but broad strokes - they
stabilize with more observations -->

@@

<!-- win  length * increasing window length = increasingly similar layers and
increasingly redundant edges. more individuals have the opportunity to interact
* increasing window length also leads to increasing similarity between seasons
because seasons are less well defined/include more shoulder seasons * decreasing
graph strength at the upper end of window length in winter showing again
inclusion of more shoulder season * layers are more similarly relevant at high
window length -->

@@

<!-- Similarly, shifting window position of the summer season resulted in an
increase in number of connections between individuals. Layer relevance  -->
<!-- win position * increasing network connectivity in summer when the window
position is moved - these seasons are more similar than the original window
position * same theme shown in the connective redundancy * quite variable layer
similarity, not sure what to pull out of that one * increased graph strength for
winter down the middle, with generally increasing summer layers - again where
the season is including more shoulder season potentially -->
<!-- Shifting window position results showed increasing layer similarity  -->
**Missing: discussion of window position..**

>>>>

# Scale in multilayer networks in practice: case study results and discussion
<!-- TODO: Add intro/general to results? with mention figures are means of inds-->
<!-- TODO: make sure we clarify these are means of all individuals? -->
<!-- TODO: discuss layer similarity for social threshold -->

In general, individuals in multilayer networks became more connected as social
scale increased; however, this relationship varied by habitat type and season.
As social scale increased, graph strength for winter networks increased to
~100-200 m thresholds, followed by a plateau, while graph strength for summer
networks did not change as the social threshold increased (Figure
\@ref(fig:socres)a). Layer relevance increased for winter networks between 5 and
50 m social thresholds, then did not change for any habitat types which suggests
the winter habitat layers captured most, if not all, of the potential
connections an individual would have across these networks (Figure
\@ref(fig:socres)b). <!-- missing summer--> Connective redundancy increased
rapidly when groups were formed up to ~100 m threshold, followed by
a plateau and slight decrease at higher thresholds, presumably due to an
increase in summer forest degree at ~500 m (Figure \@ref(fig:socres)d). Taken
together, these results suggest the optimal social scale at which groups should
be assigned is likely somewhere between ~20-100 m based on the rate at which
network metrics stabilized. For ungulates, groups are often assigned based on 50
m threshold (Lingle 2003; Lesmeries et al. 2018; Peignier et al. 2019),
suggesting that given similar quantities of data, ~50 m is likely an ideal
social scale for generating social networks in caribou and similar species.

Increasing the scale of landcover resolution resulted in decreased proportion of
rare and patchy habitats, and low connectivity of individuals in these habitats.
In winter, layer relevance was stable for open and forest habitats but decreased
for forage habitats (Figure \@ref(fig:lcres)b). Layer similarity was generally
stable for forest and open habitats except for a contrasting increase in
similarity for forest and decrease in similarity for open habitats 250 m
landcover resolution (Figure \@ref(fig:lcres)c). Layer similarity was not
possible to calculate between winter and summer forage because, at all landcover
resolutions greater than 30 m there were no individuals connected in the network
layers. <!-- individuals still used forage but in much lower proportion +
lowered opportunity to associate --> Connective redundancy decreased with
increasing landcover resolution due the decrease in connectivity of individuals
in winter forage habitats, resulting in a multilayer network where neighbours
were less frequently repeated in multiple layers <!-- TODO: I'm having a hard
time understanding this previous sentence --> (Figure\@ref(fig:lcres)d).  These
results indicate the importance of matching landcover resolution to scale of
selection as well as ensuring the landcover product used has a resolution fine
enough to detect relevant landscape features and habitats. <!-- TODO: how? This
isn't clear enough for me to follow yet -->

@@

@@

**Missing: discussion of window position..**
